Adolescent well-being in the digital age

### 2022-03-17 clean.Rmd
Also estimate model 1 for mobile

# Identify values to use in mv models
# Indicate unique ITU values for MV model
dat <- dat %>%
  # Unique values exist for each country-year, but must be given for each
  # outcome
  group_by(region, country, year, outcome) %>%
  mutate(itu = 1:n() == 1) %>%
  ungroup()

>>>>

# Identify values to use in mv models
# Indicate unique ITU values for MV model
dat <- dat %>%
  # Unique values exist for each country-year, but must be given for each
  # outcome
  group_by(region, country, year, outcome) %>%
  mutate(itu = 1:n() == 1, itum = 1:n() == 1) %>%
  ungroup()
